Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-06-25 extended_catalog/paper/extended_catalog.tex
lots of improvements

\documentclass[preprint]{aastex}

% TODO:
%   Add contours to images.
%   What other citations to add?

@@

\newcommand{\tsextpointlike}{\ensuremath{\tsext_{,\pointlike}}}
\newcommand{\tsextgtlike}{\ensuremath{\tsext_{,\gtlike}}}
\newcommand{\tsextalt}{\ensuremath{\tsext_{,\alt}}}

@@

\begin{abstract}
We present a new method for analyzing spatially extended sources with
the Fermi Large Area Telescope (LAT), the primary science instrument
on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
series of Monte Carlo studies that were done to validate this tool.
We then calculate the Fermi LAT's sensitivity to spatially exnteded
sources.  We then apply this tool to test all sources in the 2FGL Two
Year Catalog for extension.\cite{second_cat} We then report on the discovery
of XXXXXXXXXXXXXX new extended sources.
\end{abstract}

@@

Furthermore, a variety of spatially extended but otherwise unassociated
sources have been detected in the galacitc plane at \tev energies using
Air Cherenkov detectors. Most prominent was a survey of the galaictc
plane using H.E.S.S which discovered XXXXXXXXX spatially extended
sources\cite{HESS_plane_survey}.

@@

Nevertheless, morphological studies of sources in the $\gev$ energy
range using the Fermi LAT is challenging because of the significantly
energy dependent PSF and because of systematic errors in the galactic
diffuse emission. The Fermi PSF varies from over $XXXXXXXXXXXXXXX\deg$
at 100 \mev to $XXXXXXXXXXXXXXXX\deg$ at $100 \gev$ so the higher energy
photons are significantly more important for resolving a source. On
the other hand, we tend to run out of photons at higher energies so a
detailed statistical test must be used to maximize our sensitivity.

@@

Performing morphological studies of sources in the $\gev$ energy range using
the Fermi LAT is challenging primarily because of the significantly energy
dependent PSF and because of systematic errors in the
galactic diffuse emission. The Fermi PSF varies from over $XXXXXXXXXXXXXXXX\deg$
at 100 \mev to $XXXXXXXXXXXXXXXX\deg$ at $100 \gev$ and so the higher energy photons are
significantly more important for studying the shape of sources. One could
ideally look at just the highest energy photons, but the trade off is that
for typical sources many more source photons are expected at low energy.
For this reason, it is especially important to use as much of the data
as possible.

The second primary difficult in studying spatially extended sources is
systematic uncertainties in the diffuse emission. Systematic errors are
notoriously difficult and will be discussed more later, but the important
point to make here is that one of the most important diagnostic tools for
studying systematic errors is being able to iterate the analysis while
varying different parameters such as what goes into the diffuse model.

@@

A new analysis tool has been developed to address these unique
requirements for studying spatially extended sources with the Fermi
LAT. The overall approach for this analysis is to perform a maximum
likelihood analysis where the Poisson likelihood for observing the
measured counts is computed given an assumed sky model. The parameters
of the sky model are then fit by maximizing the log of the likelihood.
To study the extension of a source, one can assume a particular shape
for an extended source (e.g. a disk or Gaussian), and fit the spatial
parameters of that source.

@@

% Make an extension profile plot.
% show it in figures and describe it.

@@

% XXXXXXXXXXXXXXX This section needs work

@@

We performed a search of all Fermi sources found in the second Fermi LAT
catalog for extension.  To perform this search, we built a model of the
sky consistent with the two year catalog's model.   We used the same two
year data set running from XXXXXXXXXXX MET to XXXXXXXXXXX MET and we used
the same pass 7 instrument response function.  We used the same galactic
diffuse, isotropic diffuse, and earth limb emission model. The spectrum of
the galactic and isotropic diffuse models were refit during the analysis
while the earth limb emission was fixed to it's predicted value.

@@

\subsection{Alternate Diffuse Model Crosscheck}
\label{alt_diff_model_description}
% XXXXXXXXXXX All about using alternate diffuse model

@@

Since these sources are all included in the 2 year catalog,
we applied no special method to test these sources but used the same
pipeline that tested all other catalog sources for extension.  The results
are summarized in table~\ref{known_extended_sources}.  
%XXXXXXXXXXXXX DISCUSSION OF WHAT IS IN THE ABLE
Using photons with
energies greater than 1 \gev, our analysis succesfully fit the extension
of the LMC, SMC, IC443, W28, W30, W44, and W51C.  Using photons with 
energy above 10
\gev, we were able to succesffuly fit the extesion of HESS J1825-137.

Our analysis of MSH 15-52 using photons with energy above 10 \gev found an extension
consistent with the publisehed result, but with $\tsext=11.2$. This is
most likely because the published analysis used a larger energy range,
considering all evnets above 6\gev. Looking at all photons with
energy above 1\gev 
is problematic because of background source confusion whereas using photons
with energy above 10\gev does not have the statistics for a significant dection.

@@

The difficulty our analysis analysis had fitting the extension of several
of the already published extended sources should be used to emphasize the
overal difficultly in studying spatially extendee sources with the Fermi
LAT, especially in the crowded galactic plane. For particular sources,
it is often necessary to perform careful and specalized analysis to
correctly find and model the sources we see. We can not claim our method
is very complete, only that it is systematic and statistically rigorous.

@@

Using the same extension fitting procedure as described above, we
test these 515 AGN for extension. A histogram of the fit \tsext values
is shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is again a
$\chi^2/2$ distribution suggested by Wilks' Theorem.  This plot shows
a worse agreement with the theoretical distribution then was found
by our Monte Carlo study in figure~\ref{ts_ext_mc}.  But overall, the
distribution is good. No AGN get fit with a particularly significant
value of $\tsext$. Almost all of the AGN get fit with $\tsext<1$ and
there are very few AGN fit with large values of \tsext.  There where
only 2 AGN having $\tsext>10$.  The maximum fit $\tsext=13.7$ whereas the
maximum value expected theoeritcally for the $\chi^2/2$ distribution is
8.3. This result therefore shows that there is some systematic on our
analysis but that we understand it and that it will not significantly
cast into doubt our subsequent results.
% 8.3 number gotten from mathematica:
% PDF[ChiSquareDistribution[1], x]
% N[Solve[(1/2)*
%     Integrate[1/(E^(x/2)*(Sqrt[2*Pi]*Sqrt[x])), {x, TS, Infinity}] &=&  
%        1/515, TS]]

@@

The final possible effect causing this discrepancy is an imperfect
modeling of the PSF of the LAT.  Before launch, the LAT PSF
was determined using a Monte Carlo simulation of the detector.
After launch, a discrepancy was found using flight data above a
few \gev in the PSF measured using very bright AGN.  This result
was presented in conference and a publication is in preparation.
Subsequently, the PSF was fit empirically to these bright AGN and this
empirical parameterization is used in the Pass 7 Version 6 IRFs.\cite{
https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
}. But our current parameterization is not perfect. There are especially
lingering issues due to lackign the statistics at high energy to
validate the PSF as a function of the incident $\theta$ angle of a
photon. Since the distribution of $\theta$ angles for observing any
sources is different, the PSF for every source should be different.
It is likely that these issues could cause this systematic in the fit
value of \tsext for AGN.

@@

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
% Note about how TSext for AGN calculated with pointlike

@@

@@

\subsection{1FGL J1628.6-2419c}

A catalog source P72Y2516 located at $(l,b)=(353.09\deg, 16.79\deg)$
was found to be significantly extended when using photons between
1 \gev and 100 \gev.  The best fit extension was
$0.41\deg\pm0.05\deg$ and the extension significance was $\tsext=28.9$.
A smoothed counts map showing this source is seen in figure
\ref{1FGL_J1628.6-2419c}.

This source is in a region of remarkably complicated diffuse emission.
Even though it is 16\deg from the Galactic plane,
the source is right on top of the core of the Ophiuchus molecular cloud,
which contains massive star-forming regions that are very bright
in the infrared.  The region has abundant molecular and atomic gas
traced by CO and HI but also plenty of dark gas, the kind that
we find only by its association with dust emission.
% XXXXXXXXXXXXXXXXXXXXXXXX
% Citation needed
Embedded star-forming regions make it even more challenging to measure
the column density of dust.
% XXXXXXXXXXXXXXXXXXXXXXXX
% Citation needed
% XXXXXXXXXXXXXXXXXXXXXXXX
% Note about spectral index being typical of difuse emission
Although this region is significantly extended, we conclude that what we
are seeing is most likely an inadequacy in the diffuse $\gamma$-ray emission

\subsection{1FGL J1554.0-5345c}

Using photons with energy between 1 \gev and 100 \gev

Unidentified source likely diffuse emission.
See figure \ref{1FGL_J1554.0-5345c}.

To get a good fit of the source, we had to delete the nearby catalog sources P72Y2416 and P72Y2422

\subsection{1FGL J0823.3-4248}
Coincident with Puppis A SNR.
See figure~\ref{1FGL_J0823.3-4248}.

\subsection{1FGL J1613.6-5100c}
Near HESS Source XXXXXXXXXXXXXX.
See figure~\ref{1FGL_J1613.6-5100c}.

\subsection{1FGL J1632.9-4802c}
Near HESS Source XXXXXXXXXXXXXX.
See figure~\ref{1FGL_J1632.9-4802c}.

% XXXXXXXXXXXXXXXXXXXXXXXXXXX
% Note about uncertainty about background sources. 
% We model the northwestern source separatly
% but not the southeastern 'possible source'.

\subsection{1FGL J2020.0+4049}
Gamam Cygni SNR. Upcomming publication. 
% XXXXXXXXXXXXXXXXXXXXXXXX explain upcomming publication
See figure~\ref{1FGL_J2020.0+4049}.

\subsection{1FGL J1837.5-0659c}
Near HESS source HESS J1837. Upcomming publication???
% XXXXXXXXXXXXXXXXXXXXXXXX explain upcomming publication
See figure~\ref{1FGL_J1837.5-0659c}.

\subsection{P72Y1287}

Vela Jr. Upcomming publication.
% XXXXXXXXXXXXXXXXXXXXXXXX explain upcomming publication
See figure~\ref{Vela_Jr}.

@@

We make some conclusions about finding extended
sources with the Fermi LAT.

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/ts_ext_emin_1000.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/ts_ext/v3_emin_1000/merged.hdf5
    \end{center}
    \caption{
    The results of the Monte Carlo simulation described in section
    \ref{monte_carlo_validation} testing the null distribution of
    the likelihood ratio test for extension.  The $x$ axis of this
    plot is \tsext and the $y$ axis is the cumulative density for
    \tsext that was found by testing simulated point sources of
    various spectral models for extension. The four plots represent
    different spectral indices (for $\gamma$ of 1, 2, 2.5, and 3).
    And the different colors lines represent different fluxes chosen
    to span a representative range of Overlayed on the plot in dashed
    red is the cumulative density function of $\chi^2(\ts)/2$ which is
    suggested by Wilks' theorem as the theoretical distribution these
    curves should should follow.  Overall, it should be noted that there
    is a surprisingly good agreement between the Monte Carlo study and
    the theoeretical distribution. And for most spectral parameters, the
    Monte Carlo curve lies to the left of the theoretical curve, which
    would imply that using Wilks' Theorem as the null distribution would
    conservativly underestimate the signifcance of a source detection. In
    the rest of the paper, we use this theoretical curve to estimate
    the significance of our source detections.  What is quoted is the
    $>100$ \mev integral flux in measured in units of $\ph/\cm^2/\s$.
    For each spectral model, more information about the simulations is
    summarized in table~\ref{ts_ext_num_sims}. More
    information about this Monte Carlo analysis is presented in
    section~\ref{monte_carlo_validation}
    }\label{ts_ext_mc}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/diff_factor_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_diff_factor.py
    \end{center}
    \caption{Lalla}\label{diff_factor_sensitivity}
  \end{figure}

  \begin{figure}
    \begin{center}
      \includegraphics{mc_plots/compare_disk_gauss.pdf}
      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/compare_disk_gauss.pdf
    \end{center}
    \caption{Comparison of Disk and Gauss.
    % XXXXXXXXXXXXXXXXXXXXX
    % the overall point here is that disk looks like gauss once convolved with the psf.
    }\label{compare_disk_gauss}
  \end{figure}

  \begin{figure}
    \begin{center}
      \includegraphics{mc_plots/compare_r68.pdf}
      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_r68/v2/plot.py
    \end{center}
    \caption{Comparison of r68 for disk and gauss. This is a simulated disk source.
    % XXXXXXXXXXXXXXXXXXXXX
    % Add more to caption about htis plot.
    }\label{compare_r68}
  \end{figure}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{ic443_plots/ic443_ts_ext_vs_energy.pdf}
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/ts_ext_vs_energy/v1/ts_ext_vs_energy.py
    \caption{A plot of \tsext vs log(energy)
    for the SNR IC443, which has a typical spectral model.}
    \label{ts_ext_vs_energy}
  \end{center}
\end{figure}

>>>>

\documentclass[12pt,preprint]{aastex}
%\documentclass[preprint]{aastex}

\usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}

%#For adding line numbers:
\usepackage{lineno}
\linenumbers

@@

\newcommand{\tsextpointlike}{\ensuremath{\tsext_{,\pointlike}}\xspace}
\newcommand{\tsextgtlike}{\ensuremath{\tsext_{,\gtlike}}\xspace}
\newcommand{\tsextalt}{\ensuremath{\tsext_{,\alt}}\xspace}

@@

\begin{abstract}
We present a new method for analyzing spatially extended sources with
the Fermi Large Area Telescope (LAT), the primary science instrument
on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
series of Monte Carlo studies that were done to validate this tool.
We then calculate the Fermi LAT's sensitivity to spatially exnteded
sources.  We then apply this tool to test all sources in the 2FGL Two
Year Catalog for extension. We then report on the discovery
of XXXXXX\todo{What number should be put
here???} new extended sources.
\end{abstract}

@@

Furthermore, a variety of spatially extended but otherwise unassociated
sources have been detected in the galacitc plane at \tev energies using
Air Cherenkov detectors. Most prominent was a survey of the galaictc
plane using H.E.S.S which discovered 14 spatially extended sources
(\cite{HESS_plane_survey}).

@@

Nevertheless, morphological studies of sources in the \gev energy range
using the Fermi LAT is challenging because of the significantly energy
dependent PSF and because of systematic errors in the galactic diffuse
emission.  The Fermi PSF is determinted at lower energies by multiple
scatteering in the tracker The 68\% containment radius of the PSF is
approximatly 5.1\deg at 100 \mev  when averaged over instrumetn acceptance
and including photons which convert in either the thick or thin layers of
the tracker.  The PSF approaches a limit given by the granularity of the
tracker channeles and is 0.14\deg at 10 \gev (\cite{on_orbit_calibration}).
Therefore, the higher energy photons are significantly more important for
resolving a source but there are typically fewere of them.  So a detailed
maximum likelihood analysis must be used to maximize our sensitivity.

@@

@@

A new analysis tool has been developed to address the unique requirements
for studying spatially extended sources with the Fermi LAT. The tool
implements a maximum likelihood analysis where the Poisson likelihood
for observing the measured counts is computed for a particular sky
model. The parameters of the sky model are then fit by maximizing the log
of the likelihood.  To study the extension of a source, one can assume
a particular shape for an extended source (e.g. a disk or Gaussian),
and fit the spatial parameters of that source.

@@

\todo[inline]{Document the extension profile
shown in figure~\ref{extension_profile}.
Make an extension profile plot.
show it in figures and describe it.
}

@@

\todo{This Section Needs Work}

@@

We performed a search of all Fermi sources found in the second Fermi LAT
catalog for extension.  To perform this search, we built a model of the
sky consistent with the two year catalog's model.   We used the same two
years of data from August 4, 2008 to August 1, 2010 and we used the same
pass 7 instrument response function.  We used the same galactic diffuse,
isotropic diffuse, and earth limb emission model. The spectrum of the
galactic and isotropic diffuse models were refit during the analysis
while the earth limb emission was fixed to it's predicted value.

@@

\subsection{Alternate Diffuse Model Crosscheck}
\label{alt_diff_model_description}

To estimate systematic errors due to uncertaintly in our diffuse
emission background model, we performed an additional analysis
of our extended source candidates using an alternate diffuse
model. Our alterate model was based on the GALPROP\footnote{GALPROP
is a software package for calculating the dise Galactic $\gamma$-ray
emission based on a model of cosmic-ray propagation in the Galaxy. See
\url{http://galprop.stanford.edu/} for details and references} code
used in the Fermi LAT analysis of the isotropic diffuse emission
(\cite{isotropic_lat}).  In addition to using an alternate model, we
freeded additional compoents of this model and fit them simulatentously
with our source during the likelihood analysis. In particular,
we independently fit 7 HI rings, 7 HII rings, the inverse compoton,
and the E(B-V) residual component, and the isotropic and earth albedo
template. All told, there were 18 individual tempaltes where were all
simulatenously optimized during this analysis.

We do not expect that locally fitting tehse diffuse components would
produce a more physical model of the didffuse emission in the region.
But we do believe a source which does away when adding additional
degrees of freedom to the background model is likely spurious and so
this provides an important test of the valididity of our source.
The results of this fit for the new extended source candidates are
shown in table~\ref{alt_diff_model_results}. There is overal
good agreement between the \ts using the standard and alternate diffuse
models ($\ts_\gtlike$ and $\ts_\alt$ respectivly) and the \tsext values
(\tsextgtlike and \tsextalt respectivly).

@@

Since these sources are all included in the 2 year catalog, we applied
no special method to test these sources but used the same pipeline
that tested all other catalog sources for extension.  The results are
summarized in table~\ref{known_extended_sources}.  This table includes
the best fit position and extension. It also includes the source's
significance \ts and extension significance \tsext and the localization
error ellipse. The table also includes the best fit powerlaw spectral
model.

Using photons with energies greater than 1 \gev, our analysis succesfully
fit the extension of the LMC, SMC, IC443, W28, W30, W44, and W51C.
Using photons with energy above 10 \gev, we were able to succesffuly
fit the extesion of HESS J1825-137.
Our analysis of MSH 15-52 using photons with energy above 10 \gev found an extension
consistent with the publisehed result, but with $\tsext=11.2$. This is
most likely because the published analysis used a larger energy range,
considering all evnets above 6\gev. Looking at all photons with
energy above 1\gev 
is problematic because of background source confusion whereas using photons
with energy above 10\gev does not have the statistics for a significant dection.

@@

The difficulty our analysis analysis had fitting the extension of several
of the already published extended sources should be used to emphasize the
overal difficultly in studying spatially extendee sources with the Fermi
LAT, especially in the crowded galactic plane. For particular sources,
it is often necessary to perform careful and specalized analysis to
correctly find and model the sources we see. We can not claim our method
is complete.

@@

Using the same extension fitting procedure as described above, we
test these 515 AGN for extension. A histogram of the \tsext values
computed with \pointlike
is shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is again a
$\chi^2/2$ distribution suggested by Wilks' Theorem.  This plot shows
a worse agreement with the theoretical distribution then was found
by our Monte Carlo study in figure~\ref{ts_ext_mc}.  But overall, the
distribution is good. No AGN get fit with a particularly significant
value of $\tsext$. Almost all of the AGN get fit with $\tsext<1$ and
there are very few AGN fit with large values of \tsext.  There where
only 2 AGN having $\tsext>10$.  The maximum fit $\tsext=13.7$ whereas the
maximum value expected theoeritcally for the $\chi^2/2$ distribution is
8.3. This result therefore shows that there is some systematic on our
analysis but that we understand it and that it will not significantly
cast into doubt our subsequent results.
% 8.3 number gotten from mathematica:
% PDF[ChiSquareDistribution[1], x]
% N[Solve[(1/2)*
%     Integrate[1/(E^(x/2)*(Sqrt[2*Pi]*Sqrt[x])), {x, TS, Infinity}] &=&  
%        1/515, TS]]

@@

The final possible effect causing this discrepancy is an imperfect
modeling of the PSF of the LAT.  Before launch, the LAT PSF
was determined using a Monte Carlo simulation of the detector.
After launch, a discrepancy was found using flight data above a
few \gev in the PSF measured using very bright AGN.  This result
was presented in conference and a publication is in preparation.
Subsequently, the PSF was fit empirically to these bright AGN and this
empirical parameterization is used in the Pass 7 Version 6 IRFs.\footnote{
LAT Collaboraiton publication pending.
%https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
}. But our current parameterization is not perfect. There are especially
lingering issues due to lackign the statistics at high energy to
validate the PSF as a function of the incident $\theta$ angle of a
photon. Since the distribution of $\theta$ angles for observing any
sources is different, the PSF for every source should be different.
It is likely that these issues could cause this systematic in the fit
value of \tsext for AGN.

@@

@@

% Notes about extended Catalog sources
% Catalog used for analysis is P72Y_uw23.fits
% Compare to final catalog gll_pscP72Y_v4r2_v5r7p3_flags
%          1FGL Name - Preliminary 2FGL - 2FGL Name
% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425
% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333
% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753
% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705
% N/A                - P72Y1287         - 2FGL J0851.7-4635

@@

\subsection{2FGL J1627.0-2425}

% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425
% No modifications to background were needed

The two year catalog source 2FGL J1627.0-2425 was found to be significantly
extended when using photons between 1 \gev and 100 \gev.  The best
fit extension was $0.41\deg\pm0.05\deg$ and the best fit position is
$(l,b)=(353.09\deg, 16.79\deg)$ The source also appeared in the first
fermi catalog as 1FGL J1628.6-2419c.  and the extension significance
was $\tsext=28.9$.  A smoothed counts map showing this source is seen
in figure \ref{1FGL_J1628.6-2419c}.

This source is in a region of remarkably complicated diffuse emission.
Even though it is 16\deg from the Galactic plane,
the source is right on top of the core of the Ophiuchus molecular cloud,
which contains massive star-forming regions that are very bright
in the infrared.  The region has abundant molecular and atomic gas
traced by CO and HI but also plenty of dark gas, the kind that
we find only by its association with dust emission.\todo{Citation Needed}
Embedded star-forming regions make it even more challenging to measure
the column density of dust.\todo{Citation Needed}
\todo[inline]{Note about spectral index being typical of difuse emission}
Although this region is significantly extended, we conclude that what we
are seeing is most likely an inadequacy in the diffuse $\gamma$-ray emission

\subsection{2FGL J1551.3-5333}

% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1551.3-5333
% Sources that had to be deleted
%   * P72Y2416 - 2FGL J1554.4-5317
%   * P72Y2422 - Not in 2FGL source

The two year catalog source 2FGL J1551.3-5333 was found to be
extended using photons with energy between 1 \gev and 100 \gev.
We found an extension of $0.49\deg\pm 0.04\deg$ and an extension significance of
$\tsext=77.6$ at a position $(l,b)=(328.1387\deg,0.26\deg)$.  Figure
\ref{1FGL_J1554.0-5345c} shows a smoothed counts map of this source.

It was found in the one year catalog under the name 1FGL J1554.0-5345c.
To get a good fit of the source, we had to remove the nearby catalog
sources 2FGL J1554.4-5317 which we believed to be suprious. By looking at
the counts map, we saw no differentation in the source at the location
of the two catalog sources. We tested this region for source confusion
by comparing the increase in log likelihood fitting the region as an
extended source (\tsext=77.6) to the increase in log likelihood fitting
the region as two point sources (\tsinc=48.6).  Since the extended
hypothesis is a has a higher likelihood, we conclude that the source is
spatially extended More
information about the dual localization results for this source are
shown in table \ref{dual_localization_results}.

There are no obvious counterparts to this source. Furthermore, this
source is relativly soft with a spectral index of $2.31$ and
very close to the galacitc plane in a region of large diffuse emission.
We conclude that although this region is significantly extended, it most
likely represents unmodeled diffuse emission.
\todo[inline]{this needs more quantification/description}
\todo[inline]{Improve note about spectral check and lack of hardness}

\subsection{2FGL J0823.0-4246}

% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
% Deleted 
%  * P72Y1214 - 2FGL J0823.4-4305
%  * P72Y1210 - 2FGL J0821.0-4254

The two year catalog source 2FGL J0823.0-4246 was found to be
extended using photons with energy between 1 \gev and 100 \gev.
We found an extension of $0.37\deg$ and an extension
significance of $\tsext=49.2$.  The source was fit to a position of
$(l,b)=(260.31\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows
a smoothed counts map of this source.

This soruce is coincident with the one year catalog source named 1FGL J0823.3-4248.
To get a good fit of the source, we had to remove the nearby catalog
sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254.  We tested the 
region for source confusion by fitting the region instead as two point
sources and obtained $\tsinc=22.2$ which is smaller then \tsext.

\todo[inline]{Describe how this source is Coincident with Puppis A SNR
and give some interpretation of it.}

\subsection{2FGL J1615.2-5138}

% 1FGL J1613.6-5100c - P72Y2473         - 2FGL J1615.2-5138
% Deleted
%  *P72Y2490 - 2FGL J1520.6-5111
%  *P72Y2487 - 2FGL J1619.7-5040
%  *P72Y2496 - 2FGL J1622.8-5006
% Modify 
%  * P72Y2472 - 2FGL J1615.0-5051 - SkyDir(332.410,-0.293,SkyDir.GALACTIC)

The two year catalog source 2FGL J1615.2-5138 was found to be extended
using photons with energies between 10 \gev and 100 \gev. We foudn an
extension of $0.52\deg$ with an extension significance of \tsext=75.3.
The source was fit to a position of $(l,b)=(331.74\deg,-0.58\deg)$.
Figure~\ref{1FGL_1613.6-5100c} shows a smoothed counts map of this source.

This source is coincident with the one year catalog source named 1FGL
J1613.6-5100c. To get a good fit for the region, we had to remove from our
model the nearby catalog sources 2FGL J1520.6-5111, 2FGL J1619.7-5040,
and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region we
iterativly relocalized the source 2FGL J1615.0-5051 while fitting the
position and extension of 2FGL J1615.2-5138.  We ended up with a best
fit position of the nearby source 2FGL J1615.0-5051 having moved from
$(l,b)=(332.2684,0.043)$ to $(l,b)=(332.41,-0.29)$. This was necessary
because the initial localization of this source was done assumign that
2FGL J1615.2-5138 was modeled as several point sources.  To address
the possibility of source confusion, to compare the overal change in
likelihood fitting 2FGL J1615.2-5138 as two point sources and find
\tsinc=34.3 which is smaller then \tsext.

\todo[inline]{Interpret source as being coincident with HESS JXXX
and what the possible emission mechanism could be.}

See figure~\ref{1FGL_J1613.6-5100c}.

\todo[inline]{Describe What this source is/What HESS Source this is near}

\subsection{2FGL J1632.4-4753}

% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753
% Deleted
% * P72Y2535 - 2FGL J1631.7-4720
% * P72Y2550 - 2FGL J1636.3-4740
% * P72Y2556 - 2FGL J1638.0-4703
% * P72Y2528 - 2FGL J1630.2-4752
% * P72Y2543 - 2FGL J1634.4-4743
% * P72Y2539 - 2FGL J1632.4-4820
% * P72Y2521 - 2FGL J1628.1-4857
% * P72Y2527 - 2FGL J1630.1-4615
% * P72Y2562 - 2FGL J1639.8-4921
% Modify
% * P72Y2547 - 2FGL J1635.4-4717 - SkyDir(337.230,0.346,SkyDir.GALACTIC) 
%              (initial Position - SkyDir(337.1396,0.1433)
\todo[inline]{Describe how ROI was modified.
Note about uncertainty about background sources. 
We model the northwestern source separatly
but not the southeastern 'possible source'.}

See figure~\ref{1FGL_J1632.9-4802c}.

\todo[inline]{Describe What this source is/What HESS Source it is near}

\subsection{2FGL J2019.1+4040}

Gamam Cygni SNR.

% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2019.1+4040
% Delete:
% * P72Y3287
% * P72Y3262
% * P72Y3282
% * P72Y3260
\todo[inline]{Describe how ROI was modified}

\todo[inline]{
Describe how this source is analyzed more carefully in the paper
``A cocoon of freshly accelerated cosmic rays detected by Fermi
in the Cygnus superbubble''}

See figure~\ref{1FGL_J2020.0+4049}.

\todo[inline]{explain upcomming publication}

\subsection{2FGL J1834.7-0705}

% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1834.7-0705
% Delete:
% * P72Y2982
% * P72Y2986
% * P72Y2994
% * P72Y2993
% Modify:
% * P72Y2985 - SkyDir(25.574,0.320,SkyDir.GALACTIC)
%              (initial Position - SkyDir(,)
% * P72Y2974 - SkyDir(24.716,0.500,SkyDir.GALACTIC)
%              (initial Position - SkyDir(,)

Near HESS source HESS J1837. Upcomming publication???
\todo[inline]{Describe how ROI was modified}
\todo[inline]{Discuss the upcomming publication}
See figure~\ref{1FGL_J1837.5-0659c}.

\subsection{2FGL J0851.7-4635}

% (no 1FGL) - P72Y1287         - 2FGL J0851.7-4635

% Delete:
% * P72Y1291 - 2FGL J0853.5-4711
% * P72Y1296 - 2FGL J0855.4-4625
% * P72Y1274 - 2FGL J0848.5-4535
% * P72Y1259 - 2FGL J0842.9-4721
% * P72Y1310 - 2FGL J0901.7-4655
% * P72Y1300 - 2FGL J0858.0-4815
% Modify:
%  * P72Y1293 - 2FGL J0854.7-4501 - SkyDir(266.232,0.517,SkyDir.GALACTIC))
%              (initial Position - SkyDir(265.5705,-0.0099)

\todo[inline]{Describe how ROI was modified}

Vela Jr. Upcomming publication.
\todo[inline]{explain that Vela Jr will be described better in upcomming publication}
See figure~\ref{Vela_Jr}.

@@

\todo[inline]{This conclusion needs to be written}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/ts_ext_emin_1000.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/ts_ext/v3_emin_1000/merged.hdf5
    \end{center}
    \caption{
\todo[inline]{Shorted this caption}
    The results of the Monte Carlo simulation described in section
    \ref{monte_carlo_validation} testing the null distribution of
    the likelihood ratio test for extension.  The $x$ axis of this
    plot is \tsext and the $y$ axis is the cumulative density for
    \tsext that was found by testing simulated point sources of
    various spectral models for extension. The four plots represent
    different spectral indices (for $\gamma$ of 1, 2, 2.5, and 3).
    And the different colors lines represent different fluxes chosen
    to span a representative range of Overlayed on the plot in dashed
    red is the cumulative density function of $\chi^2(\ts)/2$ which is
    suggested by Wilks' theorem as the theoretical distribution these
    curves should should follow.  Overall, it should be noted that there
    is a surprisingly good agreement between the Monte Carlo study and
    the theoeretical distribution. And for most spectral parameters, the
    Monte Carlo curve lies to the left of the theoretical curve, which
    would imply that using Wilks' Theorem as the null distribution would
    conservativly underestimate the signifcance of a source detection. In
    the rest of the paper, we use this theoretical curve to estimate
    the significance of our source detections.  What is quoted is the
    $>100$ \mev integral flux in measured in units of $\ph/\cm^2/\s$.
    For each spectral model, more information about the simulations is
    summarized in table~\ref{ts_ext_num_sims}. More
    information about this Monte Carlo analysis is presented in
    section~\ref{monte_carlo_validation}.
    }\label{ts_ext_mc}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/diff_factor_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_diff_factor.py
    \end{center}
    \caption{
    \todo[inline]{Add Caption}
    }\label{diff_factor_sensitivity}
  \end{figure}

  \begin{figure}
    \begin{center}
      \includegraphics{mc_plots/compare_disk_gauss.pdf}
      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/compare_disk_gauss.pdf
    \end{center}
    \caption{Comparison of Disk and Gauss.
    \todo[inline]{Add Caption.
    the overall point here is that disk looks like gauss once convolved with the psf.
    }
    }\label{compare_disk_gauss}
  \end{figure}

  \begin{figure}
    \begin{center}
      \includegraphics{mc_plots/compare_r68.pdf}
      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_r68/v2/plot.py
    \end{center}
    \caption{Comparison of r68 for disk and gauss. This is a simulated disk source.
    \todo[inline]{Add more to caption about this plot.}
    }\label{compare_r68}
  \end{figure}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{ic443_plots/ic443_ts_ext_vs_energy.pdf}
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/ts_ext_vs_energy/v1/ts_ext_vs_energy.py
    \caption{A plot of \tsext vs log(energy)
    for the SNR IC443, which has a typical spectral model.
    \todo[inline]{Add more caption}
    }
    \label{ts_ext_vs_energy}
  \end{center}
\end{figure}
